---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# shepherd <img src='man/figures/logo.svg' align="right" height="300" />

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of shepherd is to make it as easy as possible to deploy an R script as an AWS Lambda endpoint.
The first version of this package will *only* support base R.
We hope to add support for further packages soon afterward.

## Installation

You can install the released version of shepherd from [CRAN](https://CRAN.R-project.org) with:

``` r
# No you can't.
# install.packages("shepherd")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jonthegeek/shepherd")
```
## Example

NONE OF THIS EXISTS YET.
The workhorse function is `deploy_script_http`.
This function creates an AWS Lambda instance with the necessary API to invoke your function.

```{r basic usage, eval = FALSE}
deploy_script_http(
  script = "my_script.R",
  lambda_function_name = "my_lambda",
  entry_point = "main_function"
)
```

## Code of Conduct

Please note that the shepherd project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
