---
title: "Getting Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(shepherd)
```

## Credentials

To use this package, you will need to provide AWS credentials.
The easiest way to do so is to set an `AWS_ACCESS_KEY_ID` and an `AWS_SECRET_ACCESS_KEY` in your .Renviron file.

```
AWS_ACCESS_KEY_ID=YOURKEYID
AWS_SECRET_ACCESS_KEY=YOURSECRETACCESSKEY
```

See the `aws.signature` and `aws.iam` packages for additional credential options.

## Your Script

Your script to deploy should be a single file, with one or more function definitions.
The functions can only use base R (hopefully this will be updated soon).

```{r sample-script}
main_function <- function(a, b, c) {
  if (!missing(a)) {
    return(a_function(a))
  } else if (!missing(b)) {
    return(b)
  } else if (!missing(c)) {
    return(c)
  } else {
    return("nothing")
  }
}

a_function <- function(a) {
  if (a == "this") {
    return("that")
  } else {
    return("another")
  }
}
```

One function should serve as the entry point into your script.
In the example, `main_function` is meant to server as the entry point.
This function will be called when the Lambda is invoked, with arguments provided by the trigger.

## Creating the Lambda

Call `deploy_script_http` to deploy your script.

```{r deploy, eval = FALSE}
deployed_script <- deploy_script_http(
  script = "my_script.R",
  lambda_function_name = "my_lambda",
  entry_point = "main_function"
)
```

If the call succeeds, `deployed_script` will contain the URL to call to invoke your function.
